### 2016-02-18 ch05-initvals/initial-values.tex
Some small changes all over the place

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/elvis-spectra.tikz}
  %TODO: simplify figure
  \caption[Measured input/output spectra of \BK{} filter.]{Input $U^{[r]}(\omega)$ and output $Y^{[r]}(\omega)$ spectra~\legref[2]{leg:SpectraMeasurement:U:single} measured using the Elvis.
  \legref[2]{leg:SpectraMeasurement:U:mean}: the mean spectra $\tilde{U}$ and $\tilde{Y}$, \legref[2]{leg:SpectraMeasurement:U:noise}: noise levels $\hat\sigma_U$ and $\hat\sigma_Y$.}
  \label{fig:SpectraMeasurement}
\end{figure}

>>>>

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/elvis-spectra.tikz}
  %TODO: simplify figure
  \caption[Measured input/output spectra of \BK{} filter.]{Average input $\tilde{U}(\omega)$ and output $\tilde{Y}(\omega)$ spectra \legref[2]{leg:SpectraMeasurement:U:mean} measured using the Elvis and the noise levels $\hat\sigma_U$ and $\hat\sigma_Y$  \legref[2]{leg:SpectraMeasurement:U:noise}.}
  \label{fig:SpectraMeasurement}
\end{figure}
